Kyoto VR MQP Paper First Draft

### 2019-09-04 paper.tex
Platforms intro para, Wikitude section

One of the biggest problems facing AR development as a whole, and one that we
ran into as well, is limited hardware. For starters, smartphone cameras present
a major limitation. Many smartphone cameras only capture images in 2D, which can
make generating AR content in a 3D world difficult without the use of QR or barcode
markers~\autocite{geospatialworld2018}. Additionally, GPS sensors on smartphones
can also be too imprecise for good AR tracking~\autocite{geospatialworld2018}.

@@

@@

>>>>

One of the major problems facing AR development as a whole, and one that we
ran into as well, is limited hardware. For starters, smartphone cameras present
a major limitation. Many smartphone cameras only capture images in 2D, which can
make generating AR content in a 3D world difficult without the use of QR or barcode
markers~\autocite{geospatialworld2018}. Additionally, GPS sensors on smartphones
can also be too imprecise for good AR tracking~\autocite{geospatialworld2018}.

@@

Before we could start working on creating our app, we first needed to decide which
AR development platform to use. Our preliminary research had shown us that there
are so many different platforms out there, all of which have been used to create
great AR apps. There were a lot of things we needed to consider before finalizing
on a platform, like what features it offered, which devices and operating systems the
app could run on, and definitely the cost. Detailed below are some of the different
platforms we considered.

@@

// TODO: Need a way to add Euro character to document; the way they are in now doesn't work

Wikitude is another major AR development kit that is very prevalent in the world
of AR development. It has over 130,000 registered AR developers, and is powering
over 30,000 AR apps across smartphones, tablets, and smart glasses~\autocite{wikitude2018}.
And it's easy to understand why Wikitude has so many registered developers
when you see the list of features it offers. Some of the features that appealed
most to us were their Instant Tracking, allowing for augmentation using flat surfaces;
Image Tracking, allowing for augmentation using one or multiple 2D images; and
Geo AR, allowing for creation of geo markers at specific locations to triggered AR
content~\autocite{wikitude2018}.

Wikitude also supports all sorts of different platforms. It supports Android, Apple,
and Windows phones and tablets, as well as smart glasses like the Epson Moverio,
Microsoft Hololens, and Vuzix smart glasses~\autocite{wikitude2018}. Additionally,
many different development frameworks are capable of running Wikitude's SDK.
According to Wikitude's website, their SDK works with Windows, Android, and iOS
development frameworks, as well as ARCore and ARKit, Flutter, Cordova, Xamarin,
and even Unity~\autocite{wikitude2018}.

From all of this information, Wikitude certainly sounds like a fantastic AR development
platform; it certainly did to us. But the issue we ran into was the cost. Wikitude is, in
fact, free for eligible startups, but given the criteria they list on their site, we were not
confident that we would qualify. Aside from this option, Wikitude offers a 30-day demo
license for €499, which is a lot for use to pay for a license that wouldn't even last for
our entire project. They also charge €1990 for their SDK Pro, and €2490 for their
SDK Pro 3D~\autocite{wikitude2018}. Given these prices, and our very limited budget
of \$0, we knew that we would have to pass on Wikitude and choose a different AR
development platform.
